---
title: "Statistical Inference Project 2 - Part 2"
author: "Daniel"
date: "1/20/2020"
output: html_document
keep_md: true
---

## Loading and preprocessing the data
Set Global Options
```{r}
knitr::opts_chunk$set(warnings=FALSE, message=FALSE, echo = TRUE)
```
<h1> Question 1 </h1>
<p>Load the ToothGrowth data and perform some basic exploratory data analyses</p>
```{r}
# Load dataset
data("ToothGrowth")
# use str function to look at data
str(ToothGrowth)
```

```{r}
# Change dose to factor
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
# Check that supp and dose are of same type 
str(ToothGrowth)
```

<h1>Question 2 </h1>
<p>Provid a basic summary of the data</p>
```{r}
# Call ggplot2
library(ggplot2)
# use summmary fct to show breakdown of dataset
summary(ToothGrowth)
# Create a boxplot graph 
ggplot(data = ToothGrowth, aes(x = dose, y = len)) + geom_boxplot(aes(fill = dose))
# Create graphics for toothgrowth from supplement type
ggplot(data = ToothGrowth, aes(x = supp, y = len)) + geom_boxplot(aes(fill = supp))
```

<h1> Question 3 </h1>
<p>Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)</p>
```{r}
# Check for difference due to different supplement type. Assume unequal variances for the two groups
t.test(len~supp, data = ToothGrowth)
``` 
<p> The p value is 0.06 and the range of the confidence interaval so we cannot reject the null hypothesis that different supplements have no effect on tooth length</p>
<p> Next, we can look at the three different doses and their effects on tooth length</p>

```{r}
# First we will break the ToothGrowth data into three subsets, one for each dose
dose0.5_1.0 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
dose0.5_2.0 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
dose1.0_2.0 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))

# Test for doses
t.test(len ~ dose, data = dose0.5_1.0)
t.test(len ~ dose, data = dose0.5_2.0)
t.test(len ~ dose, data = dose1.0_2.0)

```
<p>All three t tests produce p values under 5% and do not include 0 in their confidence intervals so we can reject the hypothesis. These test show that the length of teeth increases as you increase the dose</p>

<h1> Question 4 </h1>
<p> State your conclusions and the assumptions needed for your conclusions </p>

<h4> Conclusions </h4>
1. The type of the supplement does not effect tooth length
2. The dose given does effect tooth length

<h4> Assumptions </h4>
1. The sample population was representative of the total population
2. The experiment was performed in such a way that the doses and supplements were randomly administered